Untitled

### 2024-02-05 Manuscript/Untitled.Rmd
phylo plants

p1 = ggplot(c2, 
aes(fill=Pollinator_order, y=Proportion, x=Habitat)) + 
geom_bar(position = position_stack(reverse = TRUE), stat="identity")+
theme_bw() +
theme(legend.position = "bottom",
      plot.margin=unit(c(0,0,0,0), "mm"),
      legend.text = element_text(size=6),
      legend.key.size = unit(2, "mm"),
      legend.spacing.y = unit(0.1, "cm"),
       legend.box.spacing = unit(0, "pt"),
      axis.title = element_text(face = "bold", size = 8),
      axis.text = element_text(size=6)) +
xlab(NULL) +
scale_y_continuous(breaks = c(0.25, 0.5,0.75), labels = c("0.25", "0.5","0.75"))+
theme(strip.text.x = element_text(size = 12, face = "bold"),
    strip.background = element_rect(
color=NA, fill=NA, size=0.5, linetype="solid")) +
scale_fill_manual(values = c("#ffd67a","skyblue", "lightpink2", "tomato3"),
                  name = NULL) +
coord_flip(expand = FALSE) +
ggforce::facet_col(~ factor(Group, levels=c("Habitat","Bioregion")), space = "free", scales = "free_y") +
guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
ggtitle("(a)") +
theme(plot.title = element_text(size = 10, face = "bold",hjust = -0.25, vjust = 1))

#Unify labels
c1$Habitat = factor(c1$Habitat, levels = l2)
#Create barplot on the side
p2 =ggplot(c1, aes(Habitat, Count)) +
geom_col(fill = "black",width = 0.9) +
theme_light() +
theme(plot.margin=unit(c(0,0,0,0), "mm"),
      axis.ticks.y = element_blank(), 
  axis.text.y = element_blank(), 
      strip.text.x = element_text(size=12),
      strip.background = element_rect(
color=NA, fill=NA, size=0.5, linetype="solid"),
  axis.title = element_text(face = "bold", size = 8),
axis.text = element_text(size=6)) +
theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(),
panel.border = element_blank(),
axis.line = element_line(color = 'black')) +
scale_y_continuous(breaks = c(0, 10,20), labels = c("0", "10","20"), limits = c(0,30))+
xlab(NULL) +
ylab("Number of studies")+
theme(legend.position = "none")+
coord_flip(expand = F) +
ggforce::facet_col(~ factor(Group, levels=c("Habitat","Bioregion")), space = "free", scales = "free_y")

@@

a = plot_spacer() +  p3 + plot_spacer() + plot_layout(ncol=1, heights= c(9,10,1))
#Plot panel
p1 + p2 + a +plot_layout(widths = c(4,2, 2.5),heights= c(10,10,4), ncol=3)

>>>>

p1 = ggplot(c2, aes(fill = Pollinator_order, x = Habitat, y = Proportion)) + 
  geom_bar(position = position_stack(reverse = TRUE), stat = "identity") +
  theme_bw() +
  theme(legend.position = "bottom",
        plot.margin = unit(c(0, 0, 0, 0), "mm"),
        legend.text = element_text(size = 6),
        legend.key.size = unit(2, "mm"),
        legend.spacing.y = unit(0.1, "cm"),
        legend.box.spacing = unit(0, "pt"),
        axis.title = element_text(face = "bold", size = 8),
        axis.text = element_text(size = 6)) +
  ylab(NULL) +
  scale_x_continuous(breaks = c(0.25, 0.5, 0.75), labels = c("0.25", "0.5", "0.75")) +
  theme(strip.text.x = element_text(size = 12, face = "bold"),
        strip.background = element_rect(
          color = NA, fill = NA, size = 0.5, linetype = "solid")) +
  scale_fill_manual(values = c("#ffd67a", "skyblue", "lightpink2", "tomato3"),
                    name = NULL) +
  ggforce::facet_col(~ factor(Group, levels = c("Habitat", "Bioregion")), space = "free", scales = "free_x") +
  guides(fill = guide_legend(nrow = 2, byrow = TRUE)) +
  ggtitle("(a)") +
  theme(plot.title = element_text(size = 10, face = "bold", hjust = -0.25, vjust = 1))
#Unify labels
c1$Habitat = factor(c1$Habitat, levels = l2)
#Create barplot on the side
p2 = ggplot(c1, aes(x = Habitat, y = Count)) +
  geom_col(fill = "black", width = 0.9) +
  theme_light() +
  theme(plot.margin = unit(c(0, 0, 0, 0), "mm"),
        axis.ticks.x = element_blank(), 
        axis.text.x = element_blank(), 
        strip.text.y = element_text(size = 12),
        strip.background = element_rect(
          color = NA, fill = NA, size = 0.5, linetype = "solid"),
        axis.title = element_text(face = "bold", size = 8),
        axis.text = element_text(size = 6)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(color = 'black')) +
  scale_x_continuous(breaks = c(0, 10, 20), labels = c("0", "10", "20"), limits = c(0, 30)) +
  ylab(NULL) +
  xlab("Number of studies") +
  theme(legend.position = "none") +
  ggforce::facet_row(~ factor(Group, levels = c("Habitat", "Bioregion")), space = "free", scales = "free_x")

@@

p1/p2 + p3

#a = plot_spacer() +  p3 + plot_spacer() + plot_layout(ncol=1, heights= c(9,10,1))
#Plot panel
#p1 + p2 + a +plot_layout(widths = c(4,2, 2.5),heights= c(10,10,4), ncol=3)
